Explaining Black-Box Models through Counterfactuals

### 2023-11-16 examples/CounterfactualExplanations.jl/paper.tex
suppressing line 142 in cls related to subcaption

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners, boxrule=0pt, breakable, frame hidden, interior hidden]}{\end{tcolorbox}}\fi
